### 2015-05-11 conclusion.tex
update
rewrote conclusion

In this paper, we present \whoop, a new fully automatic approach for (i) finding data races in device drivers and (ii) accelerating bug-finding using race-related information. In the heart of our approach, we combine static lockset analysis with sound sequentialization and automated theorem proving. Our lockset analysis enforces the locking discipline that two threads accessing the same shared resource must hold at least one common lock, and reports a potential data race if this discipline is violated.

Compared to traditional data race detection tools that typically attempt to explore as many thread interleavings as feasible, and thus face scalability issues in the presence of realistic concurrent programs, \textsc{Whoop} not only entirely avoids reasoning about thread interleavings, but also allows the reuse of existing successful sequential verification techniques. The main limitation of our approach is that it can potentially report many false positives, as we over-approximate the device driver shared state. To tackle this problem, we use the race-related information that \whoop generates to speed up \corral, a state-of-the-art precise bug-finder for concurrent programs.

>>>>

In this paper we presented \whoop, a new fully automatic approach that can soundly detect all possible data races in device drivers. Compared to traditional data race detection techniques that are based on happens-before and typically attempt to explore as many thread interleavings as possible (and thus face code coverage and scalability issues), \textsc{Whoop} uses over-approximation, summarization and symbolic pairwise lockset analysis, and thus can scale well.

Exploiting the race-freedom guarantees provided by \whoop, we showed that we can achieve a sound partial-order reduction that can significantly accelerate \corral, a state-of-the-art precise bug-finder for concurrent programs. Using the combination of \whoop + \corral, we analyzed \sizeOfBenchmarks drivers from the 4.0 Linux kernel distribution, showing that our approach is efficient for race-checking and can achieve x-y speedups over vanilla \corral.
